\textbf{Beasts of Prey or Rational Animals?\\ Private Governance in Brazil's \emph{Jogo do Bicho}}

### 2018-09-15 paper-bicho/bicho.tex
add files

\chapter{Beasts of Prey or Rational Animals? Private Governance in Brazil's \emph{Jogo do Bicho}}
\label{chap:bicho}

\section{Introduction}
\label{sec:intro3}

@@

% \begin{figure}[!htbp]
%  \centering
%  \begin{minipage}[b]{0.45\textwidth}
%   \includegraphics[width=\textwidth, height=6cm]{images/bicho01.jpg}
%  \end{minipage}
%  \hfill
%  \begin{minipage}[b]{0.45\textwidth}
%   \includegraphics[width=\textwidth, height=6cm]{images/bicho02.jpg}
%  \end{minipage}
%  \caption{Left: cartoon of the Baron of Drummond and the animals of the \emph{jogo do bicho} (1896). Right: entry ticket to Rio's Zoological Garden that allowed the bearer to join the raffle. Sources: Instituto Histórico e Geográfico Brasileiro, Rio de Janeiro, Revista Illustrada, ano 21, no. 718 (1896) and Museu da Imagem e do Som, Rio de Janeiro. Reproduced in \citet[35--36]{chazkel2011laws}.}
%  \label{fig:barao}
% \end{figure}

@@

\begin{figure}[!htbp]
 \begin{tikzpicture}[->,>=stealth',shorten >=4pt,auto,node distance=3cm, semithick][h]
  % nodes %
  \node[circle,fill,inner sep=3pt,label=above right: \shortstack{Urban \\ Poverty}] (p) {};
  \node[circle,fill,inner sep=3pt,label=right: \shortstack{Jogo \\ do Bicho}, right = 8 of p] (y) {};
  \node[circle,fill,inner sep=3pt,label=below left: {Immigration}, below = 3 of p] (i) {};
  \node[circle,fill,inner sep=3pt,label=above:{Money Supply}, above = 3 of p] (m) {};
  \node[circle,fill,inner sep=3pt,label=below right:{Social Ties}, right = 3 of i] (s) {};
  \node[circle,fill,inner sep=3pt,label=above:{Weak Law Enforcement}, above = 3 of y] (l) {};
  \node[circle,fill=white, draw, outer sep=0pt, inner sep=3pt,label= left: \shortstack{Correlated \\ Background Factors}, above left = 2 of p] (u) {};
  % edges %
  \draw[->, line width = 1] (p) -- (y);
  \draw[->, line width = 1] (s) -- (y);
  \draw[->, line width = 1] (i) -- (s);
  \draw[->, line width = 1] (l) -- (y);
  \draw[->, line width = 1] (m) -- (y);
  \draw[->, line width = 1] (i) -- (p);
  \draw[->, dashed, line width = 1] (u) -- (p);
  \draw[->, dashed, line width = 1] (u) -- (m);
 \end{tikzpicture}
 \caption{Directed Acyclic Graph -- Explanatory Variables for the \emph{Jogo do Bicho}}
 \label{fig:dag}
\end{figure}

@@

% \begin{figure}[!htbp]
%  \centering
%  \begin{minipage}[b]{0.45\textwidth}
%   \includegraphics[width=\textwidth, height=6cm]{images/bicho03.jpg}
%  \end{minipage}
%  \hfill
%  \begin{minipage}[b]{0.45\textwidth}
%   \includegraphics[width=\textwidth, height=6cm]{images/bicho04.jpg}
%  \end{minipage}
%  \caption{\emph{Jogo do bicho} betting sites in 1917 and in 2011. The picture on the right shows a \emph{bicheiro}, a street-corner vendor. Sources: \citet{alecrim2012bicho} and \citet{ferrarini2011bicho}.}
%  \label{fig:banca1917}
% \end{figure}

@@

% \begin{figure}[!htbp]
%  \centering
%  \includegraphics[width=\textwidth, height=6cm]{images/bicho06.jpg}
%  \caption{Results of a \emph{jogo do bicho} draw from 09 January 2016. `Federal' means that the winning numbers were drawn by the federal government lottery. The first prize was group 14, the cat. Source: Unknown. Available at: \href{https://goo.gl/6PHV8u}{https://goo.gl/6PHV8u}. Access: December 2016.}
%  \label{fig:federal}
% \end{figure}

@@

% \begin{figure}[!htbp]
%  \centering
%  \includegraphics[width=\textwidth, height=6cm]{images/bicho05.jpg}
%  \caption{\emph{Jogo do bicho} results are fixed on light poles in Rio de Janeiro. Source: \citet{gomes1998bicho}.}
%  \label{fig:poste}
% \end{figure}

@@

% \begin{figure}[!htbp]
%  \centering
%  \includegraphics[width=.8\textwidth, height=8cm]{images/bicho07.jpg}
%  \caption{Castor de Andrade is shown celebrating after the samba school he sponsored, Mocidade Independente, won the Carnival parade in 1996. He was surrounded by colleagues and police officers. Andrade was the founding president of LIESA (1984--1985) and the wealthiest \emph{bicheiro} of Rio de Janeiro at the time. Source: Folha Imagem. Reproduced in \citet[139]{misse2007illegal}.}
%  \label{fig:castor}
% \end{figure}

@@

% \begin{figure}[!htbp]
%  \centering
%  \includegraphics[width=.6\textwidth, height=8cm]{images/bicho08.jpg}
%  \caption{Political advertising for Abraãozinho David (right), nephew of the \emph{jogo do bicho} banker Aniz Abraão David (third from left to right). The banner reads: `The Candidates of the Abraão Family: Fighting for the People is a Family Heritage'. Source: \citet{extra2012aniz}.}
%  \label{fig:aniz}
% \end{figure}

@@

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{libertine}
\usepackage{inconsolata}
\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{setspace}
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm]{geometry}
\usepackage[backref,pagebackref]{hyperref}
\usepackage{graphicx}
\usepackage{float}
\usepackage{mathtools}
\usepackage{caption}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\cleanlookdateon
\usepackage[authoryear]{natbib}
\usepackage{babelbib}
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=1000
\clubpenalty=1000
\renewcommand*{\backref}[1]{}
\renewcommand*{\backrefalt}[4]{%
	\ifcase #1 (Not cited.)%
	\or        Cited on page~#2.%
	\else      Cited on pages~#2.%
	\fi}
\renewcommand{\backreftwosep}{ and~}
\renewcommand{\backreflastsep}{ and~}
\urlstyle{same}  % don't use monospace font for urls

\hypersetup{pdftitle={Beasts of Prey or Rational Animals? Private Governance in Brazil's Jogo do bicho},
	pdfauthor={},
	pdfborder={0 0 0},
	breaklinks=true,
	linkcolor=darkblue,
	citecolor=darkblue,
	urlcolor=darkblue,
	colorlinks=true}

\doublespacing

\title{\textbf{Beasts of Prey or Rational Animals?\\ Private Governance in Brazil's \emph{Jogo do Bicho}}}

\author{Danilo Freire\thanks{Postdoctoral Research Associate, Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, \href{mailto:danilofreire@brown.edu}{\texttt{danilofreire@brown.edu}}, \href{http://danilofreire.com}{\texttt{http://danilofreire.com}}. I would like to thank Paulo Roberto Araujo, Jose Bolanos, Diogo Costa, Guilherme Duarte, Robert McDonnell, David Skarbek, the editor, and four reviewers for their helpful comments. I gratefully acknowledge the support of the National Council for Scientific and Technological Development.}
}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
 \noindent
 This work presents a rational choice account for the \emph{jogo do bicho} (`animal game'), possibly the largest illegal lottery game in the world. Over 120 years, the \emph{jogo do bicho} has grown into a multimillion-dollar business and exerted a significant impact on the Brazilian society. The lottery has been a major sponsor of the Carnival Parade in Rio de Janeiro, which is among the world's most famous popular festivals, and it has remained an important driver of state corruption in the country. This work investigates the institutions that have caused the \emph{jogo do bicho}'s notable growth and long-term survival outside the boundaries of the Brazilian law. It also explains the emergence of the informal rules that govern the game as well as their enforcement mechanisms.

 \vspace{.5cm}
 \noindent
 \textbf{Keywords}: Brazil; criminal organisations; gambling; \emph{jogo do bicho}; private governance

 \vspace{.25cm}
 \noindent
 \textbf{JEL Classification Codes}: D72, K42, Z00
\end{abstract}

\newpage

\section{Introduction}
\label{sec:intro}

@@

@@

@@

@@

@@

@@

@@

@@

\newpage

\bibliography{references}
\bibliographystyle{apalike}
\end{document}
